---
title: "Homework 9 - Alligators"
author: "Ammar Plumber, Elaina Lin, Kim Nguyen, Meghan Aines, Ryan Karbowicz"
date: "4/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Introduction
We will be examining the difference in Tweet communications between TikTok and Facebook. These are two popular social media platforms but with very different target audiences, thus the two brands could differ in their communication styles and language.

## Analysis

Loading packages.

```{r, warning = FALSE, message = FALSE}
library(rtweet)
library(tidyverse)
library(lubridate)
library(scales)
library(tidytext)
```


```{r, include = FALSE, message = FALSE, warning = FALSE, echo = FALSE}
api_key <- "0000"
api_secret_key <- "0000"
access_token <- "0000"
access_token_secret <- "0000"

token <- create_token(
  app = "Hw9-alligators",
  consumer_key = api_key,
  consumer_secret = api_secret_key,
  access_token = access_token,
  access_secret = access_token_secret)
```

Getting tweets

```{r, message = FALSE, warning = FALSE}
# Run these two lines to get the tweets 
# and then save them as a csv for future use
# tiktok <- get_timeline("tiktok_us", n=3200)
# tiktok %>% write_as_csv('tiktok.csv')
# 
# facebook <- get_timeline("Facebook", n=3200)
# facebook %>% write_as_csv("facebook.csv")

tiktok <-
  read_csv('tiktok.csv') %>% 
  select(status_id, source, text, created_at)

facebook <-
  read_csv('facebook.csv') %>% 
  select(status_id, source, text, created_at)

nrc <- read_rds("nrc.rds")

facebook %>% head()
```

```{r}
facebook %>%
  count(source, hour = hour(with_tz(created_at, "EST"))) %>%
  mutate(percent = n/sum(n)) %>%
  ggplot(aes(x = hour, y = percent, color = source)) +
  labs(x = "Hour of day (EST)", y = "% of tweets", color = "") + 
  scale_y_continuous(labels = percent_format()) +
  geom_line() +
  ggtitle('Facebook Source Breakdown by Hour')

tiktok %>%
  count(source, hour = hour(with_tz(created_at, "EST"))) %>%
  mutate(percent = n/sum(n)) %>%
  ggplot(aes(x = hour, y = percent, color = source)) +
  labs(x = "Hour of day (EST)", y = "% of tweets", color = "") + 
  scale_y_continuous(labels = percent_format()) +
  geom_line() +
  ggtitle('Tiktok Source Breakdown by Hour')
```


```{r}
fb_picture_counts <- 
  facebook %>%
  filter(!str_detect(text, '^"')) %>%
  count(picture = ifelse(str_detect(text, "t.co"),
                         "Picture/link", "No picture/link"))

tiktok_picture_counts <- 
  tiktok %>%
  filter(!str_detect(text, '^"')) %>%
  count(picture = ifelse(str_detect(text, "t.co"),
                         "Picture/link", "No picture/link"))

barplot(fb_picture_counts$n, 
        names.arg=c("No picture/link", "Picture/link"),
        main = "Facebook # of Tweets with and without pics/link")

barplot(tiktok_picture_counts$n, 
        names.arg=c("No picture/link", "Picture/link"),
        main = "Tiktok # of Tweets with and without pics/link")

```

```{r}
reg <- "([^A-Za-z\\d#@']|'(?![A-Za-z\\d#@]))"

# Unnest the text strings into a data frame of words
fb_words <- 
  facebook %>%
  filter(!str_detect(text, '^"')) %>%
  mutate(text = str_replace_all(text, 
                                "https://t.co/[A-Za-z\\d]+|&amp;", 
                                "")) %>%
  unnest_tokens(word, text, 
                token = "regex", 
                pattern = reg) %>%
  filter(!word %in% stop_words$word,
         str_detect(word, "[a-z]"))

tiktok_words <- 
  tiktok %>%
  filter(!str_detect(text, '^"')) %>%
  mutate(text = str_replace_all(text, 
                                "https://t.co/[A-Za-z\\d]+|&amp;", 
                                "")) %>%
  unnest_tokens(word, text, 
                token = "regex", 
                pattern = reg) %>%
  filter(!word %in% stop_words$word,
         str_detect(word, "[a-z]"))

# Inspect the first six rows of tweet_words
head(fb_words)
```

```{r}
fb_words %>%
  count(word, sort = TRUE) %>%
  head(20) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_bar(stat = "identity") +
  ylab("Occurrences") +
  coord_flip()

tiktok_words %>%
  count(word, sort = TRUE) %>%
  head(20) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_bar(stat = "identity") +
  ylab("Occurrences") +
  coord_flip()
```

```{r}
fb_sentiment <-    
 inner_join(fb_words, nrc, by = "word") %>% 
            group_by(sentiment)  

tiktok_sentiment <-    
 inner_join(tiktok_words, nrc, by = "word") %>% 
            group_by(sentiment) 

fb_words %>% head()
```

Here we compare the sentiment between Facebook and TikTok. It looks like Facebook uses more trust words while TikTok uses more words that reflect anticipation.
```{r}
fb_sentiment_analysis <- fb_sentiment %>% 
  count(word, sentiment) %>% 
  group_by(sentiment)

fb_sentiment_analysis %>%  
  top_n(15) %>% 
  ggplot(aes(x = sentiment, y = n )) +
  geom_bar(stat = "identity") +
  coord_flip() +
  ylab("Frequency") +
  xlab("Sentiment") +
  labs(title="Facebook Sentiment")

tiktok_sentiment_analysis <- tiktok_sentiment %>% 
  count(word, sentiment) %>% 
  group_by(sentiment)

tiktok_sentiment_analysis %>%  
  top_n(15) %>% 
  ggplot(aes(x = sentiment, y = n )) +
  geom_bar(stat = "identity") +
  coord_flip() +
  ylab("Frequency") +
  xlab("Sentiment") +
  labs(title="TikTok Sentiment")

```

